\documentclass[12pt,letterpaper]{article}

\input{style}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Mitchell Karmen} \hfill
\textsf{\small mkarmen1@jhu.edu, mitchell@nyu.edu} \\[0.5ex]
Astrophysics Graduate Student, NSF GRFP Fellow, Johns Hopkins University\\[0.5ex]

\subsection{Education}
\begin{list}{}{\cvlist}
  \item
        PhD Expected 2028, Department of Physics and Astronomy, Johns Hopkins University. Advisor: Suvi Gezari
  % \item add my masters here when I get it
  
  \item
        BA 2020, Department of Physics, New York University. Advisors: David Hogg, Sjoert van Velzen, Glennys Farrar
\end{list}

\subsection{Positions}
\begin{list}{}{\cvlist}
  \item
        Graduate Student, Johns Hopkins University, 2022--present.
  \item
        Research Assistant, Lawrence Berkeley National Lab, 2021--2022. % adding SCP makes it too long
  \item
        SULI Intern, Lawrence Berkeley National Lab, 2020--2021
  \item
        Scientific Software Developer, Zwicky Transient Facility, 2020.
\end{list}


\subsection{Publications}
% \input{pubs_summary}

\subsubsection{Refereed publications}
\begin{list}{}{\cvlist}
\input{pubs_ref}
\end{list}

\subsubsection{Preprints \& white papers}
\begin{list}{}{\cvlist}
\input{pubs_unref}
\end{list}


\subsection{Selected invited talks \& presentations}
\begin{list}{}{\cvlist}

  \item \emph{A new window into the first black holes with JWST observations of high-redshift TDEs}, \\
      2024, Contributed Talk, COSMOS-Web Collaboration Meeting, IPMU, Tokyo, Japan. \\
      2024, Contributed Talk, First Stars VII, Center for Computational Astrophysics, New York City.

  \item \emph{Enabling Discovery of High Redshift TDEs through Roman}, \\
      2023, Invited Talk, Roman Community Forum, Virtual.
      
  \item \emph{Extending the Twins Embedding for Use by the Roman/WFIRST Supernova Survey}, \\
      2021, Contributed Talk, Roman Science Team Community Briefing, Virtual.

  \item \emph{Investigating the Variability of Type Ia Supernovae Using Deep Learning}, \\
    2021, Poster, Lawrence Berkeley Lab Summer Intern Poster Session, Berkeley, CA.

  \item \emph{A New All-Sky Catalog of Compact Galaxies}, \\
    2020, Poster, American Astronomical Society Meeting 225, Honolulu, HI.

  \item \emph{A New All-Sky Catalog of Compact Galaxies: Opportunities for Electromagnetic Transient Follow-Up}, \\
    2019, Poster, Gotham AstroFest, New York, NY.

\end{list}

\subsection{Awards and Honors}
\begin{list}{}{\cvlist}

  \item NSF Graduate Research Fellowship, 2024.
  \item George Granger Brown Award (NYU), 2020.
  \item Dean's Undergraduate Research Award (NYU), 2019.

\end{list}

\ifdefined\withpubs
  \subsection{Publications}

  \subsubsection{Refereed publications}
  \begin{list}{}{\cvlist}
    \input{pubs_ref}
  \end{list}

  \subsubsection{Preprints \& white papers}
  \begin{list}{}{\cvlist}
    \input{pubs_unref}
  \end{list}
\fi

\subsection{Teaching}
\begin{list}{}{\cvlist}
  \item \emph{Physics and Astronomy Teaching Assistant} \\
      General Physics Lab II, Johns Hopkins University, 2023. \\
      Planets, Life and the Universe, Johns Hopkins University, 2022. \\
      General Physics Lab I, Johns Hopkins University, 2022.
    \item Berkeley Lab Director's Apprenticeship Program, Volunteer Coding Instructor, 2021,
    \item Department Tutor (NYU) \\
      General Physics I: Kinematics
      General Physics II: Electricity and Magnetism
    \item 7th Grade Mathematics Teaching Assistant, America Counts, 2017--2018.
\end{list}

\subsection{Outreach and Leadership}
\begin{list}{}{\cvlist}

\item \emph{Johns Hopkins University / Space Telescope Science Institute Liason} 2023--Present, \\ I lead organization of joint events between graduate students at JHU and scientists at STScI

\item \emph{Berkeley Lab Director's Apprenticeship Program}, 2021, \\ Helped to instruct low-income high school students in the basics of Python programming; mentored a small group of students in applying to college, writing application essays, etc.

\item \emph{Tampa Heights Junior Civic Association}, 2021, \\ One-on-one mentor to a low-income middle school student who is interested in science.

\item \emph{NYU Society of Physics Students} 2019--2020, \\ President

\item \emph{NYC BioBus} 2019--2020, \\ Volunteer Instuctor; Led groups of high school students through physics demonstrations
    
\end{list}

\subsection{Additional Education}
\begin{list}{}{\cvlist}
    \item Summer School in Statistics for Astronomers XVII, Penn State University, 2023.
    \item Center for Teaching Excellence and Innovation Teaching Institute, Johns Hopkins University, 2023.
    \item GROWN Multi-Wavelength Astronomy Summer School, Virtual, 2020.
    \item Data Analysis Boot Camp, Center for Computational Astrophysics, 2019.
    
\end{list}



\end{document}