% this copy of my CV is meant for continuous integration.
% it's based on dan foreman-mackey's example here https://dfm.io/posts/travis-latex/
%. style and layout from david w hogg: 
%--------------------------------------------------------------
% to-do:
%   - Sections: non-research related jobs, outreach, awards, publications, presentations, code/skills, ...
%   - Make a better template
%   - Include mentorship
%   - Include SULI presentations
% REMINDER: Don't ever push to github from here, instead push locally using this to preview.... there must be a better way
%--------------------------------------------------------------

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Mitchell Karmen} \hfill
\textsf{\small mitchell@nyu.edu} \\[0.5ex] %optional: website
Research Assistant, Supernova Cosmology Project, Lawrence Berkeley National Laboratory\\[0.5ex]

\medskip

I study Type Ia Supernovae, the explosions of white dwarf stars, and how they can inform us about the past, present, and future of our universe.  I combine astrophysical models and cutting-edge statistical models such as machine learning in order to develop methods of studying these events.  More generally, I'm interested in all kinds of extragalactic transients, and data science as it applies to time-domain astronomy.


\cvheading{Education}
\begin{list}{}{\cvlist}


  \item
        BA 2020, Physics, New York University.


\end{list}

\cvheading{Positions}
\begin{list}{}{\cvlist}


  \item
        Research Assistant, Lawrence Berkeley National Laboratory, 2021--present. \textit{Advisor: Saul Perlmutter}

  \item
        DOE Science Undergraduate Laboratory Intern, Lawrence Berkeley National Laboratory, 2020--2021. \textit{Advisor:Peter Nugent}

  \item
        Scientific Programmer, Zwicky Transient Facility Black Hole Working Group, Summer 2020. \textit{Advisor: Sjoert van Velzen}
  \item
        Undergraduate Researcher, NYU Center for Cosmology and Particle Physics, 2019--2020. \textit{Advisor: Glennys Farrar}

\end{list}

\cvheading{Administrative Roles}
\begin{list}{}{\cvlist}

\item
  President, Society of Physics Students, New York University, 2019--2020.

\item
  Treasurer, Society of Physics Students, New York University, 2017--2018.

\item
  Tutor, General Physics I and II, New York University Department of Physics, 2018--2020.


\end{list}


\cvheading{Additional Education}
\begin{list}{}{\cvlist}

\item
  GROWTH Multi-Wavelength Astronomy Summer School, 2020.


\item
  Data Analysis Bootcamp, Center for Computational Astrophysics, Flatiron Institute, 2018--2019.

\end{list}

\cvheading{Presentations}
\begin{list}{}{\cvlist}

\item
  Investigating the Variability of Type Ia Supernovae Using Deep Learning, \textit{Mitchell Karmen, Peter Nugent, Saul Perlmutter}, Lawrence Berkeley National Laboratory Intern Poster Session, Spring 2021
\item
  Unsupervised Clustering of Type Ia Supernova Lightv Curves, \textit{Mitchell Karmen, Peter Nugent}, Lawrence Berkeley National Laboratory Intern Poster Session, Fall 2020

\item
  A New All-Sky Catalog of Compact Galaxies, \textit{Mitchell Karmen, Glennys Farrar, Sjoert van Velzen}, 235th Meeting of the American Astronomical Society, 2020

\item
  A New All-Sky Catalog of Compact Galaxies, \textit{Mitchell Karmen, Glennys Farrar, Sjoert van Velzen}, Gotham AstroFest, 2019.

\item
  Finding Exoplanets in Strange Orbits, \textit{Mitchell Karmen, David Hogg}, NYU Undergraduate Research Symposium, 2018

\end{list}


\cvheading{Awards and Grants}
\begin{list}{}{\cvlist}

\item
  George Granger Brown Award, NYU Department of Physics, 2020

\item
  Conference Grant, NYU Dean's Undergraduate Research Fund, 2020.

\item
  Collegiate Research Scholar, NYU Dean's Undergraduate Research Fund, 2019

\item
  Research+ Scholar, NYU College of Arts and Sciences, 2018.

\item
  Collegiate Research Scholar, NYU Dean's Undergraduate Research Fund, 2019

\end{list}


\cvheading{Outreach}
\begin{list}{}{\cvlist}

\item
  Mentor, Tampa Heights Junior Civic Association, 2021--Present

\item
  Volunteer Instructor, BioBus, 2019--2020.

\item
  Lead Organizer, NYU Physics Mentorship Program, 2019--2020
\item
  Middle School Mathematics Teaching Assistant, America Counts, 2017--2018.

\end{list}



\end{document}
